%%%% Proceedings format for most of ACM conferences (with the exceptions listed below) and all ICPS volumes.

\documentclass[sigplan,10pt, review]{acmart}\settopmatter{printfolios=true,printccs=false,printacmref=false}

%\documentclass[sigconf]{acmart}

\usepackage{booktabs} % For formal tables
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{stmaryrd}
\usepackage{mathtools}
\usepackage[ruled]{algorithm2e} % For algorithms
\usepackage{listings}
\usepackage{subfig}

\newcommand{\todo}{\textcolor{red}{\textbf{TODO}}}
\newcommand{\var}[1]{\mathit{#1}}
\newcommand{\bv}[1]{#1~\mathit{word}}
\newcommand{\bitmoded}[2]{{\underbracket[1pt][1pt]{#2}_{#1}}}
\newcommand{\bitmodeu}[2]{{\overbracket[1pt][1pt]{#2}^{#1}}}
\newcommand{\testbit}{~!!~}
\newcommand{\nocompile}[1]{}
\newcommand{\CC}{C\nolinebreak\hspace{-.05em}\raisebox{.4ex}{\small +}\nolinebreak\hspace{-.10em}\raisebox{.4ex}{\small +}}

\DeclareMathOperator{\ucast}{zxtend}
\DeclareMathOperator{\sint}{sint}
\DeclareMathOperator{\msb}{msb}
\DeclareMathOperator{\sextend}{sxtend}
\DeclareMathOperator{\zextend}{zxtend}
\DeclareMathOperator{\rev}{rev}
\DeclareMathOperator{\bytesof}{bytes\_of}
\DeclareMathOperator{\parity}{parity}
\DeclareMathOperator{\fold}{fold}
\DeclareMathOperator{\sign}{sign}
\DeclareMathOperator{\isNaN}{isNaN}

\renewcommand{\algorithmcfname}{ALGORITHM}
\SetAlFnt{\small}
\SetAlCapFnt{\small}
\SetAlCapNameFnt{\small}
\SetAlCapHSkip{0pt}
\IncMargin{-\parindent}

\lstdefinestyle{customc}{
  language=C,
  basicstyle=\small
}

\lstdefinelanguage
   [x64]{Assembler}     % add a "x64" dialect of Assembler
   [x86masm]{Assembler} % based on the "x86masm" dialect
   % with these extra keywords:
   {morekeywords={CDQE,CQO,CMPSQ,CMPXCHG16B,JRCXZ,LODSQ,MOVSXD, %
                  POPFQ,PUSHFQ,SCASQ,STOSQ,IRETQ,RDTSCP,SWAPGS, %
                  rax,rdx,rcx,rbx,rsi,rdi,rsp,rbp, %
                  r8,r8d,r8w,r8b,r9,r9d,r9w,r9b, %
                  r10,r10d,r10w,r10b,r11,r11d,r11w,r11b, %
                  r12,r12d,r12w,r12b,r13,r13d,r13w,r13b, %
                  r14,r14d,r14w,r14b,r15,r15d,r15w,r15b}} % etc.

\lstdefinestyle{customasm}{
  belowcaptionskip=1\baselineskip,
  language=[x64]Assembler,
  basicstyle=\ttfamily,
	keywordstyle=\ttfamily,
  commentstyle=\itshape,
}

\lstset{escapeinside={(*@}{@*)},language=[x64]Assembler,style=customasm,morecomment=[l][\itshape]{\#}}


% Copyright
 \setcopyright{none}
%\setcopyright{acmcopyright}
%\setcopyright{acmlicensed}
%\setcopyright{rightsretained}
%\setcopyright{usgov}
%\setcopyright{usgovmixed}
%\setcopyright{cagov}
%\setcopyright{cagovmixed}

% DOI
\acmDOI{}
\acmISBN{}

%Conference
\acmConference[CPP'19]{ACM SIGPLAN International Conference on Certified Programs and Proofs}{January 2019}{Lisbon, Portugal}
\acmYear{2019}
\startPage{1}

\begin{document}
% Title portion. Note the short title for running heads
\title{Formally Verified Big Step Semantics out of x86-64 Binaries}

\author{Ian Roessle}
%\orcid{1234-5678-9012-3456}
\affiliation{%
  \institution{Virginia Polytechnic Institute and State University}
  \streetaddress{}
  \city{}
  \state{}
  \postcode{}
  \country{}
}
\email{iroessle@vt.edu}
\author{Freek Verbeek}
\affiliation{%
  \institution{Virginia Polytechnic Institute and State University}
  \streetaddress{}
  \city{}
  \state{}
  \postcode{}
  \country{}
}
\email{freek@vt.edu}
\author{Binoy Ravindran}
\affiliation{%
  \institution{Virginia Polytechnic Institute and State University}
  \streetaddress{}
  \city{}
  \state{}
  \postcode{}
  \country{}
}
\email{binoy@vt.edu}


\begin{abstract}
This paper presents a methodology for generating formally proven equivalence theorems between decompiled x86-64 machine code and big step semantics. 
These proofs are built on top of two additional contributions. 
First, a robust and tested formal x86-64 machine model containing small step semantics for 1625 instructions.
Second, a decompilation-into-logic methodology supporting both x86-64 assembly and machine code at large scale.
This work enables black-box binary verification, i.e., formal verification of a binary where source code is unavailable.
As such, it can be applied to safety-critical systems that consist of legacy components, or components whose source code is unavailable due to proprietary reasons.
The methodology minimizes the trusted code base by leveraging machine-learned semantics to build a formal machine model.
We apply the methodology to several case studies, including binaries that heavily rely on the SSE2 floating-point instruction set, and binaries that are obtained by compiling code that is obtained by inlining assembly into C code.
%Between the optimization of compiliers and a lack of formal instruction semantics, lifting x86-64 binaries and formaly verifying them to a specification has been fraught with difficulty. As such, most formal verification methodologies often operate at a higher level of abstraction to the binary and rely on trusted compilers. Operating systems often however leverage custom assembly or a hybrid of C++ and Assembly in order for performance, which would would not work with former approaches. Leviathan's main contribution is a step toward enabling verification at the binary level -- namely that of lifting an x86-64 binary up to big step semantics for formal verification at a more abstrat level of representation.
\end{abstract}



%
% The code below should be generated by the tool at
% http://dl.acm.org/ccs.cfm
% Please copy and paste the code instead of the example below.
%
\begin{CCSXML}

<concept>
<concept_id>10003752.10003790.10003798</concept_id>
 <concept_desc>Theory of computation~Equational logic and rewriting</concept_desc>
<concept_significance>500</concept_significance>
</concept>

<concept>
<concept_id>10003752.10003790.10011119</concept_id>
 <concept_desc>Theory of computation~Abstraction</concept_desc>
<concept_significance>500</concept_significance>
</concept>
</ccs2012>


\end{CCSXML}

 \ccsdesc[500]{Theory of computation~Equational logic and rewriting}
 \ccsdesc[500]{Theory of computation~Abstraction}

 %
% End generated code
%


\keywords{x86-64,
semantics, theorem proving}


\maketitle


% The default list of authors is too long for headers.
\renewcommand{\shortauthors}{I. Roessle et al.}


%\input{samplebody-conf}
\input{Leviathan_Body}

\bibliographystyle{ACM-Reference-Format}
%\bibliographystyle{ACM-Reference-Format}
%\bibliography{sample-bibliography}

\end{document}
